---
title: "Happiness_website"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(countrycode)
library(plotly)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
library(plotly)
library(dplyr)
```

Jiaqi Chen (jc5681),
Xinran Sun (xs2447),
Yiru Gong (yg2832),
Yunlin Zhou (yz4184)

## Data Input

```{r}
happy_df = readxl::read_xls('DataPanelWHR2021C2.xls') %>% 
  janitor::clean_names()

```


# World map of Happiness

<<<<<<< HEAD
```{r}
happy_iso3 = happy_df %>% 
  subset(
    country_name != "Kosovo" & country_name != "Somaliland region"
  ) %>% 
  mutate(
    country_code = countrycode(country_name, "country.name", "iso3c")
  ) %>% 
  relocate(country_code)
```

```{r}
plot_2018_map = happy_iso3 %>% 
  filter(year == 2018) %>% 
  plot_ly(
    type = 'choropleth', locations = ~country_code, z = ~life_ladder,
    text = ~country_name
  )

plot_2018_map
```

# Happiness score Rank

=======

```{r}
score_rank = 
  happy_df %>% 
  filter(year == "2018") %>% 
  arrange(life_ladder) %>% 
  mutate(
    country_name = factor(country_name, levels = country_name)
  )

score_rank %>% 
  plot_ly(x = ~life_ladder, y = ~country_name, color = ~country_name, type = "bar", colors = "viridis")
```


# Yearly Trend (line plot)
```{r}
yearly_trend = 
  happy_df %>% 
  filter(country_name == "Denmark" | country_name == "United States" | country_name == "China" | country_name == "Afghanistan" | country_name == "Mongolia" | country_name == "Haiti") %>% 
  ggplot(aes(group = country_name, x = year, y = life_ladder, color = country_name)) + geom_point(alpha = .5) + geom_line() 

yearly_trend
```



# Factors Related to Happiness Score

# Regression Model

