---
title: "Report"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(countrycode)
library(plotly)
library(dplyr)
library(modelr)
library(mgcv)
<<<<<<< HEAD
=======

>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

<br>

# Motivation

Scientific evidence has shown that being happy will bring positive effects on people's both mental and physical health. Staying happy promotes a person to keep a healthy lifestyle. Mentally, happiness helps people conquer stress and relieve pressure. Physically, being happy boosts people's immune system, protect their heart, and overall reduce potential pain. Happiness may even increase people's life expectancy.

From a nationwide perspective, happier citizens may have better work performance and more supportive social relationships. Specifically, if employees are satisfied with what they do and feel happy about their daily jobs, they are more likely to stay long in their positions. As the turnover rate decreases, the labor cost of companies will decrease and ultimately companies will have more money to hire more employees or expand their business. If couples feel happier staying with each other, they are less likely to get divorced. Numerous studies have shown that stable marriages are associated with a low risk of diseases, ranging from diabetes to cardiovascular and respiratory issues. Supportive social relationships also help citizens to live longer and work more effectively. 

After realizing the importance of happiness, we decided to analyze what affects happiness and in what way can we increase the overall happiness level.

<br>

# Related Work

In the beginning, we were browsing on [Kaggle](https://www.kaggle.com), trying to gain some motivation from published data and projects. Then we found a linked website called [World Happiness Report](https://worldhappiness.report). On this website, we discovered happiness reports from different countries in different years. We figured this could be an  interesting topic, so we looked up a few related articles. These articles helped us understand the significance of happiness, not only for individuals but also for overall nations. Therefore, we decided to analyze happiness with data from World Happiness Report. These inspiring articles are listed below.

* "Why Governments Should Care More about Happiness." S. Arafa, April 5, 2019. [link](https://yy3019.github.io/P8105_final_project.github.io/report.html)
* "How Being Happy Makes You Healthier." D. Coyle, August 27, 2017. [link](https://www.healthline.com/nutrition/happiness-and-health)
* "The pursuit of happiness—and its economic benefits." February 26, 2020.[link](https://drivinginnovation.ie.edu/the-pursuit-of-happiness-and-its-economic-benefits/)

<br>

# Initial Questions

Through the early stage of our study, we came up with a few questions based on the 2021 world happiness report. These questions guided us to analyze data, explore findings, and organize results. These questions are listed below.

* Which country has the highest happiness score and which country has the lowest?
* How is happiness distributed in the world? 
* What factors affect happiness score and happiness distribution?
* What can governments do to increase happiness level?

<br>

# Data Source


```{r}
happy_df = readxl::read_xls('DataPanelWHR2021C2.xls') %>% 
  janitor::clean_names()
```


<br>

# Exploratory analysis
In this part, we analyzed the basic patterns and characteristics of happiness. We used a world map to plot happiness distribution, a bar plot to show happiness score ranking, a line plot to display the  happiness score trend on a yearly base, and scatter plots to manifest the relationship between factors and happiness score.

<br>

## World map of Happiness

We decided to use `plotly` to show the happiness score around the world. We added a `country_code` column which provides the iso3 code of each country because plotly need iso3 country code to draw country map. We also deleted Kosovo and Somaliland region because they do not have corresponding iso3 code. 

```{r}
happy_iso3 = happy_df %>% 
  subset(
    country_name != "Kosovo" & country_name != "Somaliland region"
  ) %>% 
  mutate(
    country_code = countrycode(country_name, "country.name", "iso3c")
  ) %>% 
  relocate(country_code)
```

We focused on Year 2018 because we wanted to know the happiness score before COVID-19. Each country's life ladder (happiness) score is shown on the map. 

```{r}
plot_2018_map = happy_iso3 %>% 
  filter(year == 2018) %>% 
  plot_ly(
    type = 'choropleth', locations = ~country_code, z = ~life_ladder,
    text = ~country_name
  )
plot_2018_map
```

<br>

## Happiness Score Rank in 2018

We used data of 2018 to plot this graph because we wanted to know people's happiness rank before COVID-19 started. Before COVID-19 emerged, Denmark had the highest happiness score, while Afghanistan had the lowest happiness score.

```{r}
score_rank = 
  happy_df %>% 
  filter(year == "2018") %>% 
  arrange(life_ladder) %>% 
  mutate(
    country_name = factor(country_name, levels = country_name)
  )
score_rank %>% 
  plot_ly(x = ~life_ladder, y = ~country_name, color = ~country_name, type = "bar", colors = "viridis")
```

<br>

## Yearly Trend

We wanted to see countries' happiness score trend on a yearly base and chose two countries from each of three groups: high-happiness-score group, medium-happiness-score group, and low-happiness-score group to plot this graph. The selected countries are Denmark, United States, China, Mongolia, Afghanistan, and Haiti. We saw that the happiness score of countries from high-happiness-score group tends to stay stable over years and go slightly lower during COVID-19 period. The happiness score of countries from medium-happiness-score group tends to increase over years and keep increasing during COVID-19 period. The happiness score of countries from low-happiness-score group tends to fluctuate over years and decrease during COVID-19 period.

```{r}
yearly_trend = 
  happy_df %>% 
  filter(country_name == "Denmark" | country_name == "United States" | country_name == "China" | country_name == "Afghanistan" | country_name == "Mongolia" | country_name == "Haiti") %>% 
  ggplot(aes(group = country_name, x = year, y = life_ladder, color = country_name)) + geom_point(alpha = .5) + geom_line() 
yearly_trend
```



<br>
## Factors Related to Happiness Score

To better explore the relationship between all the factors and happiness score, we used the `ggplot` and `plotly` to visualize the data and present the linear regression.

```{r message = FALSE, warning = FALSE}
happy_df_fac = happy_df%>%
  filter(year < 2019)
<<<<<<< HEAD
=======

>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0
round2 = function(x){
  if(is.numeric(x))
  x= round(x, digits = 2)
  return(x)
}
<<<<<<< HEAD
=======

>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0
happy_df_fac = map_dfc(happy_df_fac, round2)%>%
  mutate(year = as.character(year))
```

```{r message = FALSE, warning = FALSE}
gg_factor = function(A,B,name){
  ggplot(happy_df_fac, aes(x = A, y = B))+
    geom_point(aes(color = year))+
    geom_smooth(method = "lm")+
    labs(
    x = name,
    y = "Happiness Score",
  )
}
```

```{r message = FALSE, warning = FALSE}
gg_log = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$log_gdp_per_capita, name = "log_gdp_per_capita")
gg_social = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$social_support, name = "social_support")
gg_healthy = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$healthy_life_expectancy_at_birth, name = "healthy_life_expectancy_at_birth")
gg_freedom = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$freedom_to_make_life_choices, name = "freedom_to_make_life_choices")
gg_generosity = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$generosity, name = "generosity")
gg_perceptions = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$perceptions_of_corruption, name = "perceptions_of_corruption")
gg_positive = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$positive_affect, name = "positive_affect")
gg_negative = gg_factor(A=happy_df_fac$life_ladder,B =happy_df_fac$negative_affect, name = "negative_affect")
```

```{r fig.height = 12, fig.width = 8, message = FALSE, warning = FALSE}
library(patchwork)
(gg_log + gg_social + gg_healthy +gg_freedom ) / (gg_generosity + gg_perceptions + gg_positive + gg_negative)
```
<<<<<<< HEAD
=======

As we can see in the plots, all the factors are related to the happiness score. People would feel happy if the country they live in have high GDP, strong social support, and they could be free to make life choices, also the country is generous and offering positive affect. On the contrary, if a country has a corrupt government, people wouldn’t be happy.
>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0

<br>

<<<<<<< HEAD
# Additional analysis
=======
# Statistical Analysis
>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0

To identify the significance of relationships and establish a regression model to predict the happiness score, we first take a look on the distribution of each variable.

```{r}
par(mfrow= c(3,3))
for (n in 3:ncol(happy_df)){
  var = names(happy_df)[n]
  pull(happy_df,n) %>% hist(main=var,xlab=var)
}
```

Here our response variable `lie_ladder` follows great bell shape and is relatively non-skewed. Most of the factors are normally distributed. Therefore we can proceed to build regression model.

<br>

## Linear Regression Model

Since all factors are continuous, we can apply fundamental multivariable linear regression (MLR) here.

```{r}
# General Model
happy_fit = happy_df %>% 
  select(-country_name,-year)
fit = happy_fit %>%
  lm(life_ladder~., data=.) %>% 
  broom.mixed::tidy()
knitr::kable(fit)
```

The result indicated that `r fit[-1,] %>% filter(p.value<0.05) %>% pull(term)` are all significantly correlated with happiness score, while `r fit[-1,] %>% filter(p.value>=0.05) %>% pull(term)` does not.

<br>

## Cross Validation

To test the model efficiency and its predictory ability, we apply 100 times of cross validation and calculate the mean value of root mean squared errors (RMSE) over 100 CVs.

```{r}
set.seed(1)
<<<<<<< HEAD
=======

>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0
cv_df = crossv_mc(happy_fit, 100) %>% 
  mutate(train = map(train,as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(linear_mod = map(train, ~lm(life_ladder ~ ., data = .x)) ) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)) )
```

```{r}
ggplot(cv_df,aes(x = "linear",y = rmse_linear)) + geom_violin()
mean_rmse = mean(pull(cv_df,rmse_linear))
mean_rmse
```

Here we can see the mean RMSE is `r mean_rmse`, which is acceptable. Therefore, the model could be used to predict the country's happiness score.

<<<<<<< HEAD
# Discussion
=======
<br>

# Discussion

>>>>>>> 3bfada5e5cc5047dc73f7e8a9ced94e6d6be93b0
