---
title: "Proposal"
author: "Yiru Gong, Jiaqi Chen, Xinran Sun, Yunlin Zhou"
date: "11/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## The group members (names and UNIs)

Jiaqi Chen (jc5681),
Xinran Sun (xs2447),
Yiru Gong (yg2832),
Yunlin Zhou (yz4184),

## The tentative project title

World Happiness' Relationship to Social Factors


## The motivation for this project

We chose this dataset because we want to analyze what factors affect people's happiness scores. Factors that are included into our consideration are country, year, GDP, healthy life expectancy at birth, freedom to make life choices, generosity, and perceptions of corruption. Our goal is to find out both direct and inverse relationships between people's heappiness and above factors. 

## The intended final products

## The anticipated data sources

```{r}
library(readxl)
happiness_data = read_excel("DataPanelWHR2021C2.xls")
```

## The planned analyses / visualizations / coding challenges

We will first visualize the global happiness score distribution with a world map and rank with bar plots. Besides, a yearly alteration line plot will be presented. Then we will investigate the relationship between happiness score and GDP, social support, life expectancy, freedom score to make life choices, Generosity, Perceptions of corruption, and interactive scatter plots with fitted curve will be ploted. 

## The planned timeline

November 16-19: Project Review Meeting
November 20-26: Writing Scripts
November 27-December 3: Report
December 4-10: Webpage and screencast
